\Large \includegraphics[height=\baselineskip]{title.png} \\ \vspace{0.65mm} \large \normalfont CSE 227: Computer Security - Spring 2017 \\ \textit{ University of California San Diego }

### 2017-06-12 docs/paper.tex
Insert screenshot into introduction
Abstract + keyword

\documentclass[letterpaper,twocolumn,10pt]{article}
\usepackage{url,epsfig}
\begin{document}

@@

\abstract{TODO}

@@

Currently, most popular browsers will show the hostname in Unicode depends on the language setting to defend IDN attack.
For example, Google Chrome\footnote{\url{https://www.google.com/chrome}} will display IDN in Unicode only if all characters of the domain names belong to only one language and this language has to be the user's preferred language.

>>>>

\documentclass[letterpaper,twocolumn,10pt]{article}
\usepackage{url,epsfig}
\providecommand{\keywords}[1]{\textbf{\textit{Keywords:}} #1}

\begin{document}

@@

\abstract{
The invention of unicode made it possible for non-English speaking people to enter the world of Internet. However, it also open up the possibilities of malicious use of url. Sometimes different letters from different languages can look almost the same depending on the font. This paper mainly summarize the previous relevant work and analyze the current circumstance of Internationalized Domain Name Homograph Attack on the Internet via statistical approach on the websites from Alexa top 1 million rankings. Through the analysis results we will be able to provide some insight on this subject.
}

\keywords{IDN, homograph, Alexa, statistics analysis} %Maybe more? or reduncdant?

@@

Currently, most popular browsers will show the hostname in Unicode depends on the language setting to defend IDN attack.
For example, Google Chrome\footnote{\url{https://www.google.com/chrome}} will display IDN in Unicode only if all characters of the domain names belong to only one language and this language has to be the user's preferred language.
\ref{screenshot} show the screenshots of the original url of \url{www.google.com} and its homograph.

\begin{figure}[t]
  \includegraphics[width=\linewidth]{google.png}
  \includegraphics[width=\linewidth]{fakegoogle.png}
  \centering
  \caption{Google(top) and its homograph(bottom) on Chrome}
  \label{screenshot}
\end{figure}
